\documentclass{llncs}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{float}
\usepackage{natbib}
\usepackage{url}
\usepackage{color}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=Java,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true
  tabsize=3
}

\title{Generating Android Intent implementation code using EMF and DSL}
\author{Ashley Davison-White, ashw@itu.dk 
      \\Agnieszka Majkowska, amaj@itu.dk
      \\Jorge Y. Castillo Rodríguez, jyur@itu.dk
      \\Marrtin Rylander, mryl@itu.dk}


\institute{IT University of Copenhagen}



\date{\today}

\begin{document}
\maketitle
\thispagestyle{plain}
\pagestyle{headings}
\setcounter{page}{1}
\pagenumbering{arabic}

 \begin{abstract}
This paper describes the process of creating a development tool for programmers using the Android platform, specifically in Intent code generation. Intents are abstract ways of describing processes to be performed, and the implementation code can be verbose and tedious to write. While the coding of Intents is not difficult to comprehend, the specifics of data types and settings for each Intent makes the process error prone. The tool we will be describing in this paper is to be seen as a case study into the MDD approach for creating a prototype that allows a programmer to insert generated code for an Intent call at a desired location in the Eclipse editor. The prototype comes in the form of a plug-in to be installed in Eclipse, which is generated based on a Domain Specific Language created using Ecore EMF models and Xtext. A Model-to-Model transformation of models developed in the DSL into models in Eclipse's Java Abstract Syntax Tree (AST) is performed using the Eclipse Java Development Tools (JDT). After conducting a proper trial testing the efficacy of using our plug-in the results were clearly indicating a remarkable cut in average implementation time.   
\\[1\baselineskip]
\textbf{Keywords.} M2M, DSL, EMF, Ecore, M2M, Xtext, Android, Intent
 \end{abstract}

\input{introduction}

\input{background}

\input{realisation}

\input{evaluation}

\input{threatstovalidity}

\input{usecases}

\input{relatedwork}

\input{futurework}

\input{conclusion}

\renewcommand{\bibname}{References}
\setlength{\bibsep}{0.0pt}
\bibliographystyle{plain}
\bibliography{references}

\end{document}